An efficient approach to approximating the pair distribution function of the inhomogeneous hard-sphere fluid

### 2014-09-02 papers/pair-correlation/paper.tex
edit conclusion paragraph Tested on bennet. Took 0:19.61.

We have introduced and tested the contact value approach for the pair
distribution function of the inhomogeneous hard-sphere fluid.  The CVA
is suitable for use in the development of classical density
functionals constructed using perturbation theory, as it may be
efficiently computed using exclusively fixed-kernel convolutions.  We
have tested this function at a hard wall and near a single fixed hard
sphere, and find that it gives qualitatively reasonable results.
Tests of the pair distribution function in integrals that arise in
thermodynamic perturbation theory suggest that the CVA is accurate for
attractions up to the distance to which the radial distribution
function is fit, and is an improvement over existing approximations
near contact.

>>>>

We have introduced and tested the contact value approach for the pair
distribution function $g^{(2)}(\rr_1,\rr_2)$ of the inhomogeneous
hard-sphere fluid.  The pair distribution function plays a key role in
thermodynamic perturbation theory, which is widely used in the
construction of classical density functionals.  The CVA---unlike
existing approximations---is suitable for use in classical density
functionals based on perturbation theory, as it may be efficiently
computed using exclusively fixed-kernel convolutions.  We have tested
this function at a hard wall and near a single fixed hard sphere, and
find that it gives excellent agreement with simulation.  Tests of the
pair distribution function in integrals that arise in thermodynamic
perturbation theory suggest that the CVA is accurate for attractions
up to the distance to which the radial distribution function is fit,
and is a significant improvement over existing approximations near
contact.  But most importantly, the computational cost of using the
CVA in a classical density functional scales much more favorably than
existing methods in high resolution computations.
